The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-23 paper.tex
update

  We tabulate parameters in the \textbf{Isothermal disk} and \textbf{Atmosphere}\
  categories in \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\

@@

  \begin{enumerate}
     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
     \item Using PyFC code to obtain the clumpy cuboid $\rho_{\text{clumpy}}$ obeying\
           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \times \rho_{\text{isoDisk}}(\bf{x})$.
     \item
  \end{enumerate}

>>>>

  We tabulate parameters in the first four\
  categories in \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\

@@

  \begin{enumerate}
     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(\bold{x})$ by \Cref{isothermal-disk-density}.
     \item Using PyFC code to obtain the clumpy cuboid $\rho_{\text{clumpy}}$ obeying\
           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
     \item $\rho_{\text{ismDisk}}(\bf{x}) = \rho_{\text{clumpy}}(\bf{x}) \rho_{\text{isoDisk}}(\bf{x})$.
     \item
  \end{enumerate}
